Online {\IterComp}

### 2017-11-17 motivation.tex
minor changes

    Typical single-run performance metrics, like runtime or Instructions Per Cycle~(IPC), are not fit for purpose. To show this, we
    performed iterative compilation on \texttt{tiff2bw}, evaluating each optimization sequence on a different input and using either
    runtime or IPC as our efficiency metric. We selected a set of ten inputs from the KDataSets. When
    iterative compilation is driven by runtime, the selected optimization slows down the benchmark by 3\% compared to \texttt{-O3}. When
    driven by IPC, it is even worse with an average slowdown of 49\%. Its very high IPC of 3.25 does not indicate high performance. The
    actual best optimization over the whole input set improves performance by 7\% while only having an average IPC of 2.31.
   Higher IPC does not necessarily translate to better performance,
 different optimizations affect IPC in different ways.
   Similarly, a shorter runtime may be due to inputs with fewer work for the program to process.

\begin{table}[h]
\centering
\label{tab:motivation_metrics}
\begin{tabular}{|l|l|l|}
\hline
\multicolumn{1}{|c|}{Metric} & \multicolumn{1}{c|}{Speedup/Slowdown} & \multicolumn{1}{c|}{IPC} \\ \hline
Oracle (Speedup)             & 7\% speedup                                 & 2.31                      \\ \hline
IPC                          & 49\% slowdown                                & 3.25                      \\ \hline
1/Runtime                    & 3\% slowdown                                  & \multicolumn{1}{c|}{-}   \\ \hline
\end{tabular}
\caption{Comparison of iterative compilation guided by different metrics.
The oracle is guided by the average speedup over \texttt{-O3} on all inputs.
For IPC and runtime, each optimization was evaluated on a different input.
}
\vspace{-2ex}
\end{table}

>>>>

    Typical single-run performance metrics, like runtime or Instructions Per Cycle~(IPC), are not fit for purpose. To show this, we
    performed iterative compilation on \texttt{tiff2bw}, evaluating each optimization sequence on a different input and using either
    runtime or IPC as our efficiency metric. We selected a set of ten inputs from the KDataSets. When
    iterative compilation is driven by runtime, the selected optimization slows down the benchmark by 3\% compared to \texttt{-O3}. When
    driven by IPC, it is even worse with an average slowdown of 49\%. Its very high IPC of 3.25 does not indicate high performance. The
    actual best optimization over the whole input set improves performance by 7\% while only having an average IPC of 2.31.
   Higher IPC does not necessarily mean better performance,
 different optimizations affect IPC in different ways.
   Similarly, a shorter runtime may be due to inputs with fewer work to process.

\begin{table}[h]
\centering
\label{tab:motivation_metrics}
\begin{tabular}{|l|l|l|}
\hline
\multicolumn{1}{|c|}{Metric} & \multicolumn{1}{c|}{Speedup/Slowdown} & \multicolumn{1}{c|}{IPC} \\ \hline
Oracle (Speedup)             & 7\% speedup                                 & 2.31                      \\ \hline
IPC                          & 49\% slowdown                                & 3.25                      \\ \hline
1/Runtime                    & 3\% slowdown                                  & \multicolumn{1}{c|}{-}   \\ \hline
\end{tabular}
\caption{Comparison of iterative compilation guided by different metrics.
The oracle is guided by the average speedup over \texttt{-O3} on all inputs.
For IPC and runtime, each optimization was evaluated on a different input.
}
\end{table}

### 2017-11-17 results.tex
minor changes

We also evaluate the actual cost perceived by the user when applying online iterative compilation.
To this end we used the architecture described in Section~\ref{sec:oic-infra} with the search based on genetic algorithm~\cite{knijnenburg02,cooper99,kulkarni04}.
Our results provide evidence that the proposed approach is profitable in real-world online scenarios.
Figure~\ref{fig:deployment_cost} shows, for each benchmark and configuration, the profitability of the final optimization sequence
selected by the search (as in Figure~\ref{fig:speedups}) but also the average profitability/cost experienced by the user throughout the search process (labeled as [Live]),
which takes into account the overhead of the work profiling.

>>>>

We also evaluate the actual cost perceived by the user when applying online iterative compilation.
To this end we used the architecture described in Section~\ref{sec:oic-infra} with the search based on genetic algorithm~\cite{knijnenburg02,kulkarni04}. %cooper99
Our results provide evidence that the proposed approach is profitable in real-world online scenarios.
Figure~\ref{fig:deployment_cost} shows, for each benchmark and configuration, the profitability of the final optimization sequence
selected by the search (as in Figure~\ref{fig:speedups}) but also the average profitability/cost experienced by the user throughout the search process (labeled as [Live]),
which takes into account the overhead of the work profiling.
